---
title: "Figures for MMM Manuscript"
author: "Mauna Dasari"
date: "10/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse);library(gridExtra);library(scales)
theme_set(theme_minimal())
```

# Fig1: Scholarly Literature {.tabset}
## A Battle Citations By Year
```{r}
df1A<-read.csv("Data/Fig1/NumberCitationsYear.csv")
df1A[is.na(df1A)]<-0
colnames(df1A)<-c("Year","Battle Narration", "Genetics")
df1A<-df1A %>% pivot_longer(-Year,names_to = "Type",values_to = "citations")
df1A$Type<-factor(df1A$Type,
                    levels = c("Genetics","Battle Narration"))

plot1A<-ggplot(df1A,aes(x=as.factor(Year),y=citations))+
    geom_col(aes(fill=Type),color="black")+
    xlab("Year")+ylab("Number of Citations")+
    scale_y_continuous(breaks = seq(0, 500, by = 50),
                       expand = c(0,0))+
    scale_fill_manual(values=c("#7B287B","#3C557C"))+
    labs(title="A. Battle Citations by Year")+
    theme(plot.title = element_text(hjust = 0.5,size=16),
          legend.position = c(.2,.8),
          legend.title = element_blank(),
          axis.text = element_text(size=10),
          axis.title = element_text(size=13),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4));plot1A
```

## B Battle Narration Top 25 Cited Journals
```{r}
df1B<-read.csv("Data/Fig1/CitationsByJournal.csv",stringsAsFactors = T)
colnames(df1B)<-c("Publication","Citations")
jlevel<-levels(df1B$Publication)

plot1B<-ggplot(df1B,aes(x=fct_reorder(Publication,Citations),y=Citations))+
    geom_col(fill="#3C557C",color="#212F45",width = 1)+ #teal: 206E83
    ylab("Number of Citations")+
    coord_flip()+
    labs(title="B. Top 25 Journals Cited in Narrations")+
    theme(plot.title = element_text(hjust = .5,size=16),
          axis.text.y = element_text(size=10),
          axis.title.x = element_text(size=13),
          axis.title.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4));plot1B
```

## C Publication Year of Citations
```{r}
df1C<-read.csv("Data/Fig1/CitationsYears.csv")
colnames(df1C)<-c("Year","Citations")

plot1C<-ggplot(aes(x=Year,y=Citations),
               data=df1C)+
    geom_col(fill="#3C557C",color="#212F45",width = 1)+ #lighter teal 029597
    ylab("Number of Citations")+
    #xlab("Year")+
    scale_x_continuous(breaks = pretty_breaks(n=12),expand = c(0,0))+
    scale_y_continuous(breaks = pretty_breaks(n=10),expand = c(0,0),position = "left")+
    labs(title="C. Publication Year of Citations Used in Narrations")+
    theme(axis.text.x = element_text(angle = 90,
                                     vjust = 0.5, 
                                     hjust=1,
                                     size=10),
          axis.text.y = element_text(size=10),
          axis.title = element_text(size=13),
          plot.title = element_text(hjust = .5,size=16),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank());plot1C
```

## Combo
```{r fig.height=7,fig.width=15}
library(patchwork)
patchedfig1<-((plot1A / plot1C ) | plot1B) + plot_layout(guides = 'keep')#+plot_annotation(tag_levels = 'A')
patchedfig1
ggsave("FullPlots/Fig1Citations.png", width=15,height=7,dpi=300)
```

# Fig2: Species Representation
```{r}
fig2colors<-read.csv("Data/Fig2.csv") %>% select(Class,HexCode)

df2<-read.csv("Data/Fig2.csv") %>% 
    select(Class,Class.Representation,March.Mammal.Madness) %>% 
    rename("Mammalian Class" = Class.Representation,
           "March Mammal Madness" = March.Mammal.Madness) %>% 
    pivot_longer(-Class,names_to="Category",values_to = "Represented") %>% left_join(fig2colors,by="Class")

sorted<-df2 %>% 
    filter(Category=="Mammalian Class") %>% 
    arrange((Represented)) %>% 
    pull(Class)
sorted_colors<-df2 %>% 
    filter(Category=="Mammalian Class") %>% 
    arrange(desc(Represented)) %>% 
    pull(HexCode)
df2$Class<-factor(as.character(df2$Class),levels=sorted)
df2$HexCode<-factor(as.character(df2$HexCode),levels=as.character(sorted_colors))
df2$HexCode<-fct_rev(df2$HexCode)

plot2<-ggplot(df2,aes(x=Category,y=Represented,fill=Class))+
    geom_bar(stat="identity",color="black")+
    scale_fill_manual(name="Class",values=as.character(df2$HexCode));plot2
```

# Fig3: Outcome Proportions
```{r}
df3<-read.csv("Data/Fig3.csv")
colnames(df3)[1]<-"Outcome"

df3<-df3 %>% 
    pivot_longer(-Outcome,names_to = "Year",values_to = "Percent") %>% 
  mutate(Percent=Percent/100)
df3$Year<-gsub("X","",as.character(df3$Year))
df3$Outcome<-factor(df3$Outcome,levels=c("Other","Deus ex Machina","Withdrawal","TKO"))

plot3<-ggplot(df3,aes(x=Year,y=Percent,fill=Outcome))+
    geom_bar(stat="identity",color="black")+
    scale_fill_manual(values=c("#90BE6D","#577590","#F9C74F","#F94144"))+
    #scale_x_discrete(expand = c(0,0))+
    scale_y_continuous(expand = c(0,0),labels = scales::percent)+
    labs(title="Battle Outcomes by Tournament Year")+
    theme(legend.position="bottom",
          legend.title = element_blank(),
          axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=10),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = .5,size=16),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())+
  guides(fill = guide_legend(reverse = TRUE));plot3

ggsave("FullPlots/Fig3Outcomes.png", width=7,height=5,dpi=300)
```

# Fig5: Student Reach
## A Regional Reach
```{r}
df5A<-read.csv("Data/Fig5A.csv")
colnames(df5A)<-c("Region","US K-12 Public School Population","US K-12 Students Engaged in Mammal March Madness")

df5A<-df5A %>% 
    pivot_longer(-Region,names_to = "Category",values_to = "Percent")
df5A$Region<-factor(df5A$Region,levels=c("Pacific","Northeast & Mid-Atlantic","Great Lakes","Mountain West & Midwest Plains","South Central","South Atlantic"))

plot5A<-ggplot(df5A,aes(x=Category,y=Percent,fill=Region,label=Percent))+
    geom_bar(stat="identity",color="black",width=.75)+
    geom_text(size = 4, 
              position = position_stack(vjust = 0.5),
              aes(label = sprintf("%1.2f%%", 100*Percent,
                                  fontface="bold")))+
    scale_fill_manual(values=c("#43aa8b","#61a8fa","#577590","#f9c74f","#f3722c","#f94144"))+
    scale_x_discrete(labels = function(Category) str_wrap(Category, width = 20))+
    scale_y_continuous(expand = c(0,0),
                     labels = scales::percent)+
    labs(title="A. Student Population Distribution: Geographic Regions")+
    theme(legend.position="right",
          legend.title = element_blank(),
          axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=10),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = .25,size=16),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank());plot5A

ggsave("FullPlots/Fig5A.png",dpi=300)
```

## B Region Type
```{r}
df5B<-read.csv("Data/Fig5B.csv")
colnames(df5B)<-c("Region","US K-12 Public School Population","US K-12 Students Engaged in Mammal March Madness")

df5B<-df5B %>% 
    pivot_longer(-Region,names_to = "Category",values_to = "Percent")
df5B$Region<-factor(df5B$Region,levels=c("Urban","Suburban","Rural"))

plot5B<-ggplot(df5B,aes(x=Category,y=Percent,fill=Region,label=Percent))+
    geom_bar(stat="identity",color="black",width=0.55)+
    geom_text(size = 4, 
              position = position_stack(vjust = 0.5),
              aes(label = sprintf("%1.2f%%", 100*Percent,
                                  fontface="bold")))+
    scale_fill_manual(values=c("#C19EE0","#A06CD5","#815ac0"))+
    #scale_x_discrete(expand = c(0,0))+
    scale_x_discrete(labels = function(Category) str_wrap(Category, width = 20))+
    scale_y_continuous(expand = c(0,0),
                     labels = scales::percent)+
    labs(title="B. Student Population Distribution: Rural, Suburban, and Urban")+
    ylab("Percentage")+
    theme(legend.position="right",
          legend.title = element_blank(),
          axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=10),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = .25,size=16),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank());plot5B
ggsave("FullPlots/Fig5B.png", dpi=300)
```

## Combo
Did this in powerpoint
```{r eval=F}
library(magick);library(ggpubr)
map <- image_read('FullPlots/MapChart_Map.png')
twitter <- ggplot() +
  background_image(map) 
twitter

library(patchwork)
patchedfig5<-((plot5A / twitter ) | plot5B) + plot_layout(guides = 'keep')#+plot_annotation(tag_levels = 'A')
patchedfig5
ggsave("FullPlots/Fig1Citations.png", width=15,height=7,dpi=300)
```

# Fig 6 LibGuide Traffic
## Bracket Drop = Day 0
```{r}
library(gridExtra);library(grid)

df6<-read.csv("Data/LibGuideTraffic.csv") 
colnames(df6)[1]<-"Day"
phase<-df6 %>% select(Day,Phase)

df6<-df6 %>% 
  select(-Phase) %>% 
  pivot_longer(-Day,names_to="Year",values_to="Pageviews")
df6$Year<-as.factor(gsub("X","",as.character(df6$Year)))

Text1<-textGrob("Bracket Drop")

plot6<-ggplot(data=df6,aes(x=Day,y=Pageviews,group=Year,color=Year))+
  geom_line(size=1)+#,aes(linetype=Year)
  scale_color_manual(values=c("#F9C74F", "#F8961E","#F94144"))+
  #ylim(0,70000)+
  scale_y_continuous(labels = comma,expand=c(0,0),
                     breaks = pretty_breaks(n=8),limits = c(0,60000))+
  scale_x_continuous(breaks=pretty_breaks(n=8),limits = c(-4,35))+
  labs(title = "Mammal March Madness ASU LibGuide Daily Pageviews")+
  xlab("Day")+ylab("Number of Pageviews")+
  geom_segment(aes(x=0,y=53500,xend=10,yend=53500,color="segment"),
               color="black",linetype="solid")+
  geom_segment(aes(x=0,y=0,xend=0,yend=53500,color="segment"),
               color="black",linetype="dashed")+
  geom_segment(aes(x=10,y=0,xend=10,yend=53500,color="segment"),
               color="black",linetype="dashed")+
  annotate(geom="text",x=5,y=57000,size=4,lineheight=.85,
           label="Pre-Tournament \n Species Research Period")+
  geom_segment(aes(x=10,y=10000,xend=34,yend=10000,color="segment"),
               color="black",linetype="solid")+
  geom_segment(aes(x=34,y=0,xend=34,yend=10000,color="segment"),
               color="black",linetype="dashed")+
  annotate(geom="text",x=22,y=12500,size=4,lineheight=.85,
           label="Tournament")+
  theme(legend.position = "bottom",
        legend.text = element_text(size=13),
        plot.title = element_text(hjust = 0.5,size=16),
          legend.title = element_blank(),
          axis.text = element_text(size=11),
          axis.ticks = element_line(size = 1), 
          axis.title = element_text(size=13),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4));plot6

ggsave("FullPlots/LibGuideTraffic.png", dpi=300)
```

## Bracket Drop = Day -10
```{r}
df6<-read.csv("Data/LibGuideTraffic2.csv") 
colnames(df6)[1]<-"Day"
phase<-df6 %>% select(Day,Phase)

df6<-df6 %>% 
  select(-Phase) %>% 
  pivot_longer(-Day,names_to="Year",values_to="Pageviews")
df6$Year<-as.factor(gsub("X","",as.character(df6$Year)))


plot6<-ggplot(data=df6,aes(x=Day,y=Pageviews,group=Year,color=Year))+
  geom_line(size=1)+#,aes(linetype=Year)
  scale_color_manual(values=c("#F9C74F", "#F8961E","#F94144"))+
  #ylim(0,70000)+
  scale_y_continuous(labels = comma,expand=c(0,0),
                     breaks = pretty_breaks(n=8),limits = c(0,60000))+
  scale_x_continuous(breaks=pretty_breaks(n=8),limits = c(-14,27))+
  labs(title = "Mammal March Madness ASU LibGuide Daily Pageviews")+
  xlab("Day of Tournament")+ylab("Number of Pageviews")+
  geom_segment(aes(x=-10,y=53500,xend=0,yend=53500,color="segment"),
               color="black",linetype="solid")+
  geom_segment(aes(x=0,y=0,xend=0,yend=53500,color="segment"),
               color="black",linetype="dashed")+
  geom_segment(aes(x=-10,y=0,xend=-10,yend=53500,color="segment"),
               color="black",linetype="dashed")+
  annotate(geom="text",x=-5,y=57000,size=4,lineheight=.85,
           label="Pre-Tournament \n Species Research Period")+
  geom_segment(aes(x=0,y=10000,xend=24,yend=10000,color="segment"),
               color="black",linetype="solid")+
  geom_segment(aes(x=24,y=0,xend=24,yend=10000,color="segment"),
               color="black",linetype="dashed")+
  annotate(geom="text",x=12,y=12500,size=4,lineheight=.85,
           label="Tournament")+
  theme(legend.position = "bottom",
        legend.text = element_text(size=13),
        plot.title = element_text(hjust = 0.5,size=16),
          legend.title = element_blank(),
          axis.text = element_text(size=11),
          axis.ticks = element_line(size = 1), 
          axis.title = element_text(size=13),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4));plot6

ggsave("FullPlots/LibGuideTraffic_TournamentDay.png", dpi=300)
```

# Fig7: Twitter Engagements
```{r}
df7A<-read.csv("Data/TwitterEngagements.csv")
colnames(df7A)[1]<-"Year"
df7C<-read.csv("Data/BlogpostViews.csv")
colnames(df7C)[1]<-"Year"

plot7A<-ggplot(data=df7A,aes(x=Year,y=Number.of.Tweets))+
  geom_line()+geom_point()+ylim(35000,47000)+
  ylab("Number of Tweets Using MMM Hashtag")+
  scale_x_continuous(breaks=pretty_breaks(n=3))+
  scale_y_continuous(labels = comma)+
  labs(title="B. Mammal March Madness Twitter Engagements:\n Tweets Using the MMM Hashtag")+
  theme(plot.title = element_text(hjust = 0.5,size=16),
          legend.title = element_blank(),
          axis.text = element_text(size=11),
          axis.ticks = element_line(size = 1), 
          axis.title = element_text(size=13),
          axis.title.x = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4));plot7A
plot7B<-ggplot(data=df7A,aes(x=Year,y=Twitter.Timeline.Deliveries))+
  geom_line()+geom_point()+ylim(700000000,1400000000)+
  ylab("Number of Twitter Timeline Deliveries")+
  scale_x_continuous(breaks=pretty_breaks(n=3))+
  scale_y_continuous(labels = comma,breaks=pretty_breaks(n=8))+
  labs(title="C. Mammal March Madness Twitter Engagements:\n Deliveries to Twitter Timelines")+
  theme(plot.title = element_text(hjust = 0.5,size=16),
          legend.title = element_blank(),
          axis.text = element_text(size=11),
          axis.ticks = element_line(size = 1), 
          axis.title = element_text(size=13),
          axis.title.x = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4));plot7B
plot7C<-ggplot(data=df7C,aes(x=Year,y=Blogpost.Views))+
  geom_line()+geom_point()+ylim(20000,300000)+
  ylab("Number of Blogpost Views")+
  scale_x_continuous(breaks=pretty_breaks(n=7))+
  scale_y_continuous(labels = comma,breaks=pretty_breaks(n=8))+
  labs(title="A. Mammal March Madness Blogpost Engagements")+
  theme(plot.title = element_text(hjust = 0.5,size=16),
          legend.title = element_blank(),
          axis.text = element_text(size=11),
          axis.ticks = element_line(size = 1), 
          axis.title = element_text(size=13),
          axis.title.x = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4));plot7C
```
```{r fig.width=18,fig.height=5}
library(patchwork)
patchedfig7<-plot7C+ plot7A + plot7B + plot_layout(guides = 'keep')#+plot_annotation(tag_levels = 'A')
patchedfig7
ggsave("FullPlots/Fig7Engagements.png", width=18,height=5,dpi=300)
```

## Fig 7 Two Axes
```{r}
df7A<-read.csv("Data/TwitterEngagements.csv")
colnames(df7A)[1]<-"Year"
#df7A<-df7A %>% 
#  pivot_longer(-Year,names_to="Engagement_Type",values_to="Use")
plot7A<-ggplot(data=df7A,aes(x=Year,y=Number.of.Tweets))+
  geom_line()+geom_point(pch=15,size=3)+ylim(35000,47000)+
  ylab("Number of Tweets Using MMM Hashtag")+
  scale_x_continuous(breaks=pretty_breaks(n=3))+
  scale_y_continuous(labels = comma)+
  labs(title="B. Mammal March Madness Twitter Engagements")+
  geom_line(aes(y=Twitter.Timeline.Deliveries/3000))+
  geom_point(aes(y=Twitter.Timeline.Deliveries/3000),pch=24,size=3)+
  scale_y_continuous(sec.axis = sec_axis(~.*3000,
                                         name="Number of Twitter Timeline Deliveries"),
                     labels = comma,
                     breaks=pretty_breaks(n=8))+
  theme(plot.title = element_text(hjust = 0.5,size=16),
          legend.position = "bottom",
          axis.text = element_text(size=11),
          axis.ticks = element_line(size = 1), 
          axis.title = element_text(size=13),
          axis.title.x = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.line.x = element_line(size=.4),
          axis.line.y = element_line(size=.4));plot7A
```

```{r fig.width=12,fig.height=5}
library(patchwork)
patchedfig7<-plot7C+ plot7A + plot_layout(guides = 'keep')#+plot_annotation(tag_levels = 'A')
patchedfig7
ggsave("FullPlots/Fig7Engagements_DoubleAxis.png", width=12,height=5,dpi=300)
```
